RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-03 doc/paper.tex
Statistics: described

\begin{itemize}
	\item \fxnote{TODO}
\end{itemize}

>>>>

\begin{itemize}
	\item  Concerning instance problems where for the input data no noise is included, \textsc{Rils}-\textsc{Rols} method has the best average ranking in terms of   exact percentage rate.  The second best ranking is achieved by \textsc{AI-Feynman} algorithm. There is no statistically significant difference between these two approaches. However, these two approaches perform statistically significantly better than the third best (according the the average raking), that is with \textsc{Apf-Fe}. This conclusion also holds for the remaining approaches. 
	\item    Concerning instance problems where for the input data a (white) noise of 0.001 is included, \textsc{Rils}-\textsc{Rols} method has the best average ranking in terms of the exact percentage rate.   The second best ranking is achieved by \textsc{Afp-Fe} algorithm. However,  there is no statistically significant difference between these two approaches. The third best according approach is \textsc{Afp}, which perform statistically equal to \textsc{Afp-Fe}, but statistically worse that our \textsc{Rils}-\textsc{Rols} method. For all remaining methods, the later conclusion also holds.
	\item   Concerning instance problems where for the input data a (white) noise of 0.01 is included, again, \textsc{Rils-Rols} reaches the best average ranking; the second best approach is \textsc{gplearn}. The difference between the exact percentages delivered by these two approaches is significant in favor of \textsc{Rils-Rols} approach. This is also the case when \textsc{Rils-Rols} is compared to all the remaining approaches.
